Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-30 demystify.tex
updates

If a student asks me to write letter for them, I will agree as I believe it is part of my job.  However, I will let them know if I won't be able to write a strong letter for them (e.g., they just take my class and I don't know them well enough or they have not done much research with me), and suggest they find someone else.  If they insist, then I will write the letter, but it will likely be a weak one.  However, I will still try to write something positive about the student, e.g., they are hardworking, or that I heard they are working on a research project, etc.  I usually ask the student to provide me with some details about themselves, e.g., their GPA and transcript,  and use that to write the letter.  Regardless, the letters will still be short and weak (\autoref{sec:generic-letters}) and usually take about 5-10 minutes to write.

For students who I know well, i.e., strong letters, then it will take a lot longer as it will be personalized.  While I have a general template of such strong letters, it still can take me an hour or more to write such a letter.  I also often ask the students to provide information (\autoref{sec:help-your-LOR-writers}) and what they think I should highlight in the letter. If they already have a draft of their SOP, they can also provide that to me so I can complement what they say with my own perspective.  I also offer to review their SOP and provide feedback.

%I do ask the students to waive their right to see the letter, as it is a standard practice and a way of keeping things straightforward and respectful in the whole recommendation game.  I also let them know that I will not show them the letter, even if they do not waive their right.  I also let them know that I will not write a letter for them if they do not waive their right, as I believe that such letters are not useful and might even hurt their application.

>>>>

If a student asks me to write letter for them, I will agree as I believe it is part of my job.  However, I will let them know if I won't be able to write a strong letter for them (e.g., they just take my class and I don't know them well enough), and suggest they find someone else.  If they insist, then I will write the letter. It will be a weak and generic letter though I still try to have something positive, e.g., the student is hardworking, or that I heard they are working on a research project, etc.  Regardless, the letters will still be short and weak (\autoref{sec:generic-letters}) and usually take about 5--10 minutes to write.

For students who I know well, i.e., strong letters, then writing will take a lot longer as it will be personalized.  While I have a general template of such strong letters, it still can take me an hour or more to write such a letter.  I often ask the students to provide information (\autoref{sec:help-your-LOR-writers}) and what they think I should highlight in the letter. They can also provide me their SOP (if they already have written one) so I can complement what they say with my own perspective.
